---
title: "Developing Data Products  Pitch"
author: "Scott Fan"
date: "09/08/2018"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(knitr)
library(plotly)
library(dplyr)
library(jpeg)
set.seed(0)
usedcarsdat <- read.csv("https://www.engineeringbigdata.com/wp-content/uploads/usedcars.csv")
link <- "https://cdn.images.autoexposure.co.uk/AETA52860/AETV98414245_1.jpg"
download.file(link,'y.jpg', mode = 'wb')
jj <- readJPEG("y.jpg",native=TRUE)
##plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
##rasterImage(jj,0,0,1,1)
```

## Background

Car-buyers have many options when it comes to buying cars. They can decide to buy a brand new car off the dealership or decide to purchase a car from the resale market. This Shiny application aids car buyers in purchasing used cars. There will be several criterias that car users can choose from. 

This will draw data from the `usedcars` dataset available here. <https://www.engineeringbigdata.com/wp-content/uploads/usedcars.csv>

## Features

There will be a few features included to help car-buyers narrow down their choice. These include:

- Price range (slider)
- Mileage (slilder)
- Transmission Type (option button)

## Sample Output

```{r choice}
car_choice <- usedcarsdat[1,]
car_choice
##plot(0:1,0:1,type="n",ann=FALSE,axes=FALSE)
##rasterImage(jj,0,0,1,1)
```

```{r plot, message=FALSE, warning = FALSE}
thiscar <- usedcarsdat[1,3]
last300price <- rnorm(n=300,-500,500) + thiscar
last300time <- c(-299:0)
last300price[300] = thiscar-1000
last300 <- data.frame(Time=last300time, Price=last300price)
x <- list(
  title = "Time"
)
y <- list(
  title = "Price"
)
p<- plot_ly(last300, x=last300$Time, y=last300$Price,mode = "lines") %>%
  layout(xaxis = x, yaxis = y, width = 750, height = 300)

p

```

## Thank You



